lifespan_eda

### 2023-12-03 lifespan_eda.Rmd
adding sex.age hard-coded int term

#drop repeat scans
cn.df.unique <- cn.df %>%
  drop_na(c(age_days, participant, study)) %>%
  arrange(age_days) %>%
  group_by(participant) %>%
  slice(1) %>%
  ungroup()

>>>>

#drop repeat scans
cn.df.unique <- cn.df %>%
  drop_na(c(age_days, participant, study)) %>%
  arrange(age_days) %>%
  group_by(participant) %>%
  slice(1) %>%
  ungroup() %>%
  mutate(sexMale = as.numeric(case_when(sex == "Male" ~ 1,
                                        sex == "Female" ~ 0,
                                        TRUE ~ NA)),
         sex.age = sexMale*age_days)
